Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-01-17 PaperVictor.tex
Segunda version revisada

% !TeX spellcheck = en_US
\documentclass{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{showkeys}
\usepackage{ragged2e}
\usepackage{cite}
\usepackage{authblk}
\usepackage{xcolor}
\usepackage{braket}
\newif{\ifmover}
\newif{\ifquitar}
\renewcommand{\Affilfont}{\small}
\newcommand{\notaL}[1]{{\color{orange}L: #1}}
\newcommand{\notaVA}[1]{{\color{orange}VA: #1}}
\newcommand{\notaV}[1]{{\bf \em \color{orange}VCG: #1}}
\definecolor{Addtext}{RGB}{0,0,255}
\begin{document}

%\title{Thickness optimization in wide range quasi omnidirectional multilayer
% structures}
\title{Optimization of wide-band quasi-omnidirectional 1-D photonic structures}
\author[1,2,3]{Victor Castillo-Gallardo\thanks{email: {\tt
			victor1\_1@hotmail.com}}}
\author[1,2,3]{Luis Eduardo Puente-D\'{i}az}
\author[4]{D. Ariza-Flores}
\author[3]{Hector P\'{e}rez-Aguilar}
\author[2]{W. Luis Moch\'{a}n\thanks{email: {\tt
			mochan@fis.unam.mx}}}
\author[1]{Vivechana Agarwal\thanks{email: {\tt
			vagarwal@uaem.mx}}}
\affil[1]{Centro de Investigaci\'{o}n en Ingenier\'{i}a y
Ciencias Aplicadas, Universidad del Estado de Morelos, Av.
Universidad 1001, Col. Chamilpa, Cuernavaca, Morelos 62209,
M\'{e}xico.}
\affil[2]{Instituto de Ciencias F\'{i}sicas, Universidad
Nacional Aut\'{o}noma de M\'{e}xico, Av. Universidad S/N,
Col. Chamilpa, 62210 Cuernavaca, Morelos, México.}
\affil[3]{Facultad de Ciencias Fìsico Matem\'{a}ticas,
Universidad Michoacana de San Nicol\'{a}s de Hidalgo, Av.
Francisco J. Múgica S/N 58030, Morelia, Mich., M\'{e}xico.}
\affil[4]{CONACyT-Universidad Aut\'{o}noma de San Luis
Potosì, Karakorum 1470, Lomas 4ta Secc, San Luis Potos\'{i},
S.L.P., 78210, M\'{e}xico.}
%\date{{\small {\today}}}
\maketitle

\begin{abstract}
Porous silicon (PS) is a very versatile material for developing optical
devices based on multilayered structures, since high and low porosity layers
can be synthesized by a simple electrochemical technique. We
maximize the average \notaV{Agregue} reflectance $\braket{R}$ \notaL{El promedio no depende
  de lambda ni theta, y prom es castellano}   of PS-based
mirrors within \notaV{Agregue y quite "averaged over"} a wide wavelength
and angular range, for different
porosity contrasts, and we minimize their thickness. Optimization is
performed in the visible (Vis) and near infrarred (NIR) regions of the
electromagnetic spectrum. We design the mirrors using \textit{chirped}-type
structures and by \textit{stacking} sub-mirrors. We find \notaL{No
  estoy seguro del tiempo} that
chirped structures are more suitable for the Vis range, while stacked
sub-mirrors are better for the NIR region. \notaV{Corregi oracion} We design, fabricate and test some
optimized omnidirectional structures with less than 100
periods.
\end{abstract}

@@

Photonic crystal (PC)-based \notaL{Lo cambié de PhC, pues en otros
  casos abrevias photonic con sólo la P, como en PBG, no PhBG.}
structures have been extensively investigated due
to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
Photons entering a PC interact with its periodically varying dielectric constant and
are consequently organized into photonic bands. Analogous to electrons in a
crystal, their propagation is \notaV{Quite "will be"} forbidden if their energy lies
within certain regions known as photonic band gaps (PBG's). Thus, the
PC behaves as a mirror if illuminated by light with frequencies
withinin a PBG. For several applications it is useful to fabricate
{\em ommnidirectional} mirrors with a wide band gap.  The use of metallic
mirrors is limited due to their relatively large absorption at
visible and near infrared frequencies.  An attractive alternative
consists of low-absorption dielectric
structures,  which may be designed for specific frequency
ranges. One-dimensional (1D) and two-dimensional (2D) PCs have
applications in optoelectronics, optical telecommunications and computing,
laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
\cite{Kumar2020}. The simplest 1D-PC is composed of a finite number
of periodically alternating
layers of high $n_{H}$ and low $n_{L}$ refractive indices, with
corresponding thicknesses $d_H$ and $d_L$ chosen so that their optical
thicknesses are \notaV{Modifique "of is"} quarter-wavelength
$n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$ at a \notaV{Quite "some chosen"} nominal
wavelength $\lambda_{0}$. This yields a {\em Bragg mirror} (BM)
which might have a large PBG including an omnidirectional gap if the contrast $n_H/n_L$
and the number of periods are large enough. Mirrors with high
reflectance within a wider frequency range may be engineered by
using different nominal wavelengths for different layers.
One way to obtain such structures is to gradually change the width of
the layers as a function of their depth, producing
\textit{chirped}-type structures \cite{Zipock1997}.
Another alternative is to stack BMs, in such a way that their reflection bands partially
overlap each other at the edge, resulting in a wider high-reflection band \cite{Xifre2009}.
\notaV{Se modifico la oracion "An alternative is to stack BM's, such that their PBG
overlap each other, resulting in a wider high-reflection band"}. 
\notaL{No me convence la redacción. ¿No la revisó Vivechna?} \notaL{Para un
  espejo de Bragg, el ancho de banda de reflexión coincide (a incidencia normal)
  con la brecha prohibida, pero para los 'chirped' y los 'stacked',
  que no son periódicos, tal vez 'brecha prohibida' no es un buen
  término. Más bien, queremos hablar del ancho de banda del espejo,
  i.e., la región en que es buen reflector.}

On the other hand, different fabrication techniques have been used to obtain omnidirectional
mirrors (ODM) that operate on the visible and/or near infrared (Vis-NIR) range of the
electromagnetic spectrum. \notaV{Se modifico la oracion "Till now, different deposition 
techniques have been used to obtain omnidirectional BM (ODBM) that operate on 
the visible and near infrared (Vis-NIR) range of the electromagnetic spectrum."} 
For example, Chen et al. \cite{Chen1999},
\notaL{Hay que checar que la puntuación vaya después de las citas,
  para este estilo de citas entre corchetes} reported the fabrication of a 
6-pair TiO$_{2}$/SiO$_{2}$ structure \notaV{Se cambio "have reported"} with
 an OD band of about 70 nm in the NIR range, employing sol-gel deposition 
method. Park et al. \cite{Park2003}, used molecular beam epitaxy to 
grow a stack of four pairs of GaAs/AlAs layers, followed by its conversion to
GaAs/Al$_{2}$O$_{3}$ layers by selective oxidation of the AlAs 
layers, to obtain an OD with a band from 710 to 950 nm. 
On the other hand, DeCorby et al. \cite{DeCorby2005}, fabricated mirrors by
coupling multiple layers of Ge$_{33}$As$_{12}$Se$_{55}$ chalcogenide glass and
polyamide-imide polymer, deposited by thermal evaporation and spin-casting
respectively, to obtain a 150 nm wide omnidirectional band centered at
1750 nm. Furthermore, Jena et al. \cite{Jena2019},
used sequential asymmetric bipolar pulsed DC magnetron sputtering (for TiO$%
_{2}$ layers) and radio frequency magnetron sputtering (for SiO$_{2}$
layers) to generate TiO$_{2}$/SiO$_{2}$ 1D-PC's and achieved an OD band from
592 to 668 nm. However, these techniques are expensive and they
require sophisticated equipment and long fabrication times. Using PS
is an attractive alternative, since it can be easily manufactured by 
electrochemical etching of crystalline Si in a hydrofluoric 
acid based electrolyte, to obtain a sponge-like nanostructure composed 
of Si and air. By modulating the supplied current and its application 
time to the electrochemical reaction, it is possible to obtain 
multilayer structures allowing for fabrication ODM \cite{Xifre2015,Pavesi2000}.
\notaV{Se replanteo la idea "as PS may be fabricated by simple
electrochemical etching during short times of
crystalline Si in a hydrofluoric acid based electrolyte, to obtain the
sponge-like nanostructure composed of Si and air. By modulating in
time the applied current, the porosity of the PS, and thus its
refractive index, can be modulated
along its depth. This allows the design and fabrication of 1D-PC's with PS, to
control the propagation of light in a dielectric medium. The low cost and
ease of fabrication of PS make it an excellent candidate to develop
multilayered optical devices."}
Although optical filters \cite{Estevez2009,Ariza2014} are the most common
application of PS PC's, they have also been widely used as chemical
sensors \cite{Giusseppe2011,Agarwal2018}, waveguides \cite{Hussel1997} and
for photoluminescence control \cite{Antunez2014}. Recently, the study of
chirped multilayer structures \notaV{Modifique "quasi-omnidirectional Bragg mirrors"} has
increased due to their possible application as flat focusing mirrors \cite{Wu2021,Kozar2017,Cheng2018}.
\notaL{Lens o mirror, no puede ser ambas? De verdad esto es lo que más lo ha popularizado?} 
PS based dielectric optical filters, quasi-ODBM and ODBM have been extensively studied in different
regions of the electromagnetic spectrum, such as the ultraviolet (UV)
\cite{Jimenez2020}, visible \cite{Ariza2012}, and NIR \cite{Bruyant2003}. 
However, to obtain the desirable high index of refraction
contrast, layers of high porosity have to be employed, so that the
resulting structures may be fragile, making large structures, with a
very large number of layers, unfeasible. For this reason, in this work
we study different strategies to produce multilayer \notaV{photonic} mirrors
that have a large reflectance omnidirectional band \notaV{over a wide band-width}
with relatively small thickness and refractive index contrast. 
\notaV{Se omite la frase "Specifically, our aim is to maximize the 
reflectance $R$ averaged over a wide range of wavelengths $\lambda$ 
and angles of incidence $\theta$", la idea general esta en la oracion anterior}

This paper is organized as follows. In Sec. \ref{s:theory} \notaL{No uses números,
  usa referencias a etiquetas para numerar y referir todo} we develop the
methods used to design and calculate the reflectance spectra of the PS
multilayered structures such as chirped structures and mirror
stacks. In Sec. \ref{s:exp} we provide details about the
fabrication of these structures. In Sec. \ref{s:res} we present the numerical
and experimental results for our proposed structures and compare
them to previous reports. We obtained significantly larger band-widths
with significantly thinner structures. \notaL{Dejo para resultados y
  conclusiones los detalles de con quién comparamos y qué salió.}
Finally, we discuss our conclusions in Section \ref{s:conc}.

\section{Theory}\label{s:theory}

\notaL{Pon etiquetas a todo para poderlo referir}
For the analysis of the propagation of electromagnetic fields through
multilayer systems it is usual to employ the transfer matrix
method \notaL{reference} \cite{Pochi2005, Ariza2011} \notaV{Agregue dos referencias}. 
Assuming the system is 1D, with variations
only along the $z$ directions, and that the polarization of light is either
transverse electric (TE) or transverse magnetic (TM)\notaL{si no, la matriz
  sería de 4x4}, the
transfer matrix $M\left(z_{2},z_{1}\right)$ is
a 2x2 matrix that relates the components of the electric $E_{\| }$
and magnetic  $H_{\|}$ fields parallel to the $xy$ plane
evaluated at $z_2$ to their value at $z_{1}$,
\begin{equation*}
\left(
\begin{array}{c}
E_{\|} \\
H_{\| }%
\end{array}%
\right) _{z_{2}}=M\left( z_{2},z_{1}\right) \left(
\begin{array}{c}
E_{\| } \\
H_{\| }%
\end{array}%
\right) _{z_{1}}.
\end{equation*}%
Many equivalent formulations have been proposed to obtain and use $M$
\cite{Mochan1987,Ortiz2020,Chavez2020}. Here we use a recently developed formalism
for the numerically stable calculation of the reflectance of large
multilayer systems, as
proposed by Puente-Díaaz, et al. \cite{Puente2020}, summarized in the
supplementary information. The
explicit expressions for the optical coefficients are:
\begin{equation}
r=\mp \frac{Z_{0}M_{11}+M_{12}-Z_{0}Z_{s}M_{21}-Z_s
M_{22}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{rBloch}
\end{equation}%
and
\begin{equation}
t=\frac{2Z_{\alpha
  }}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{tBloch}
\end{equation}%
where $M_{ij}$ \notaL{Quité las tildes, pues hubiera sido necesario
  explicarlas, y no creo que sean importantes para el lector} \notaV{Tiene raz\'{o}, esto se debe diferenciar en la informacion suplementaria} are the elements
of the transfer matrix which transfer
the fields from its surface interface with vacuum at $z_0$ towards the
substrate at $z_s$,  $Z_0$ is the surface impedance of vacuum and $Z_s$ is the
surface impedance of the substrate, and we define $r=F_r/F_i$ and $t=F_t/F_i$ in terms
of the reflected and transmitted fields, where we choose the $F$'s as electric
fields for (TE) polarization and magnetic fields
for transverse magnetic polarization (TM). The upper sign $-$ in
Eq. (\ref{rBloch}) and the subscript $\alpha =s$
in Eq. (\ref{tBloch}) are chosen for the case of TE polarization, while
the lower sign $+$ and the subscript $\alpha =0$ correspond to TM
polarization, respectively.
The reflectance is given by
$R=|r|^{2}$ and the
transmittance by $T=\beta \left\vert t\right\vert ^{2}$ with $\beta
=\text{Re}Z_{0}/\text{Re}Z_{s}$ for TE polarization and $\beta =\text{Re}Z_{s}/\text{Re}Z_{0}$ for
TM polarization.\notaL{En el cálculo, ¿tomaste las partes reales? No
  estaban en la fórmula} \notaV{Realmente inclu\'{i} la transmitancia solo por completez (no inclu\'{i} c\'{a}lculo alguno)} The complex refractive index of the porous
layers were obtained through the Bruggeman's effective medium theory, which
has been reported to adequately reproduce the PS optical parameters
\cite{Giusseppe2011,Pap2006,Estrada2018}.

\notaL{Creo que esto debería estar más adelante:
  After the next section, two techniques are developed to design multilayer
photonic structures. In the first, the wavelength ($\lambda _{j}$), at which
the $j$-th period of the structure is designed, is modulated by an
increasing function. This can be as simple or complex as you like. The
proposed function was optimized with the Minuit module of PDL (Perl Data
Language) \cite{minuit}. The other technique for proposing highly reflective
structures over a wide region of the electromagnetic spectrum is to stack
sub-mirrors tuned to different wavelengths. For each sub-mirror the
dispersion relation is analyzed.
} \notaV{De acuerdo}

@@

Some of the proposed photonic structures were synthesized through anodic
etching of a (100) oriented, $p$-type Boron doped, crystalline Si wafer with
resistivity 0.002-0.005 $\Omega \cdot $cm, under galvanostatic conditions
\cite{Canham1990,Escorcia2007}. The electrochemical anodization process was
performed at room temperature, with an electrolyte of aqueous
hydrofluoric acid (HF) (48$\%$ of
wt) and ethanol (99.9$\%$ of wt) in 1:1 volumetric proportion, respectively.
With this electrolyte, the minimum and maximum porosities that can be
obtained are 35$\%$ and 76$\%$ \notaL{Creo que se puede quitar de
  aquí, pues lo discutes abajo:(gravimetrically obtained)}, using
current densities of 0.5 and $305\text{mA}/\text{cm}^{2}$,
respectively. However, as it is not desirable to use very high
porosity contrasts due to structure fragility and electrolyte
diffusivity problems \cite{Ariza2011}, the current
densities were chosen as 35 and $305\text{mA}/\text{cm}^{2}$, with
corresponding
porosities of 51\% and 76\%, respectively. The porosity was calibrated
\notaL{Creo que no muestras curvas de calibración: calibration curves were
acquired} through a gravimetric technique as follows: single layers of porous
silicon were synthesized under similar conditions applying a constant
current for a time \notaL{cuánto tiempo para la calibración?}  and were weighed to
obtain their mass $m_i$
before ($m_{1}$) and after ($m_{2}$) the electrochemical attack, and after
dissolving the already formed porous silicon layer ($m_{3}$), to obtain
the porosity as $p=(m_{1}-m_{2})/(m_{1}-m_{3})$ \cite{Pap2006}.
The etching
rate of PS was obtained by synthetizing single layers under similar
conditions and measuring their thicknesses through Scanning Electron
Microscopy (SEM). Absolute reflectivity measurements were carried out
with a Perkin Elmer Lambda 950 UV/Visible spectrophotometer with a variable
angle universal reflectance accessory (URA) for different incident
angles $\theta _{i}=10^{\circ }$, $20^{\circ }$, $30^{\circ }$,
$40^{\circ }$, $50^{\circ }$ and $60^{\circ }$ using non-polarized light. The maximum and
minimum values of $\theta _{i}$ were constrained by the angular range of the
equipment accessory URA.

@@

In this section we presents optimized calculations of the reflectance
of different multilayered omnidirectional wide-band mirrors and we
compare the results to spectra taken from
the corresponding samples at several angles of
incidence. Sec. \ref{ss:chirped} is devoted to chirped-type Bragg
mirrors while Sec. \ref{ss:stacked} is devoted to structures made of
stacked sub-mirrors.

\notaL{Quizás esto se pueda incluir por aquí.:
  After the next section, two techniques are developed to design multilayer
photonic structures. In the first, the wavelength ($\lambda _{j}$), at which
the $j$-th period of the structure is designed, is modulated by an
increasing function. This can be as simple or complex as you
like. {\tiny The
proposed function was optimized with the Minuit module of PDL (Perl Data
Language) \cite{minuit}.} The other technique for proposing highly reflective
structures over a wide region of the electromagnetic spectrum is to stack
sub-mirrors tuned to different wavelengths. For each sub-mirror the
dispersion relation is analyzed.
}
\subsection{Chirped-type Bragg mirrors}\label{ss:chirped}

>>>>

% !TeX spellcheck = en_US
\documentclass{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{showkeys}
\usepackage{ragged2e}
\usepackage{cite}
\newif{\ifmover}
\newif{\ifquitar}
\usepackage{authblk}
\renewcommand{\Affilfont}{\small}
\usepackage{xcolor}
\newcommand{\notaL}[1]{{\color{orange}L: #1}}
\newcommand{\notaVA}[1]{{\color{orange}VA: #1}}
\newcommand{\notaV}[1]{{\bf \em \color{green}VCG: #1}}
\definecolor{Addtext}{RGB}{0,0,255}
\begin{document}

%\title{Thickness optimization in wide range quasi omnidirectional multilayer
% structures}
\title{Optimization of wide-band quasi-omnidirectional 1-D photonic structures}
\author[1,2,3]{Victor Castillo-Gallardo\thanks{email: {\tt
			victor1\_1@hotmail.com}}}
\author[1,2,3]{Luis Eduardo Puente-D\'{i}az}
\author[4]{D. Ariza-Flores}
\author[3]{Hector P\'{e}rez-Aguilar}
\author[2]{W. Luis Moch\'{a}n\thanks{email: {\tt
			mochan@fis.unam.mx}}}
\author[1]{Vivechana Agarwal\thanks{email: {\tt
			vagarwal@uaem.mx}}}
\affil[1]{Centro de Investigaci\'{o}n en Ingenier\'{i}a y
Ciencias Aplicadas, Universidad del Estado de Morelos, Av.
Universidad 1001, Col. Chamilpa, Cuernavaca, Morelos 62209,
M\'{e}xico.}
\affil[2]{Instituto de Ciencias F\'{i}sicas, Universidad
Nacional Aut\'{o}noma de M\'{e}xico, Av. Universidad S/N,
Col. Chamilpa, 62210 Cuernavaca, Morelos, México.}
\affil[3]{Facultad de Ciencias F\'{i}sico Matem\'{a}ticas,
Universidad Michoacana de San Nicol\'{a}s de Hidalgo, Av.
Francisco J. Múgica S/N 58030, Morelia, Mich., M\'{e}xico.}
\affil[4]{CONACyT-Universidad Aut\'{o}noma de San Luis
Potos\'{i}, Karakorum 1470, Lomas 4ta Secc, San Luis Potos\'{i},
S.L.P., 78210, M\'{e}xico.}
%\date{{\small {\today}}}
\maketitle

\begin{abstract}
Porous silicon (PS) is a very versatile material for developing optical
devices based on multilayered structures, since high and low porosity layers
can be synthesized by a simple electrochemical technique. In the present work, the 
average reflectance $<$R$>$ of PS-based mirrors is maximized within a wide 
wavelength and angular range, for different porosity contrasts. Optimization is 
performed to maximize the reflectance for minimum  thickness of the structure in the 
visible (Vis) and near infrarred (NIR) regions of the electromagnetic spectrum.   The 
mirrors are designed using \textit{chirped}-type structures and \textit{stacking} 
sub-mirrors. The chirped structures are found to be more suitable for the Vis range, 
while stacked sub-mirrors are found to be better for the NIR region. Design, fabrication 
and testing of some optimized omnidirectional structures with less than 100 periods has 
been demonstrated.
\end{abstract}

@@

Photonic crystal (PC)-based structures have been extensively investigated due
to their light controlling properties \cite{Joannopoulos2008,Goyal2018}.
Photons entering a PC interact with its periodically varying dielectric constant and
are consequently organized into photonic bands. Analogous to electrons in a
crystal, their propagation is forbidden if their energy lies
within certain regions known as photonic band gaps (PBG's). Thus, the
PC behaves as a mirror if illuminated by light with frequencies
within in a PBG. For several applications it is useful to fabricate
{\em ommnidirectional} mirrors with a wide band gap.  The use of metallic
mirrors is limited due to their relatively large absorption at
visible and near infrared frequencies.  An attractive alternative
consists of low-absorption dielectric
structures,  which may be designed for specific frequency
ranges. One-dimensional (1D) and two-dimensional (2D) PCs have
applications in optoelectronics, optical telecommunications and computing,
laser technology \cite{Lopez2003,Masaya2010}, and radiative cooling applications
\cite{Kumar2020}. The simplest 1D-PC is composed of a finite number
of periodically alternating
layers of high $n_{H}$ and low $n_{L}$ refractive indices, with
corresponding thicknesses $d_H$ and $d_L$ chosen so that their optical
thicknesses are quarter-wavelength
$n_{H}d_{H}=n_{L}d_{L}=\lambda_{0}/4$ at a nominal
wavelength $\lambda_{0}$. This yields a {\em Bragg mirror} (BM)
which might have a large PBG including an omnidirectional gap if the contrast $n_H/n_L$
and the number of periods are large enough. Mirrors with high
reflectance within a wider frequency range may be engineered by
using different nominal wavelengths for different layers.
One way to obtain such structures is to gradually change the width of
the layers as a function of their depth, producing
\textit{chirped}-type structures \cite{Zipock1997}.
Another alternative is to stack BMs, in such a way that their reflection bands partially
overlap each other at the edge, resulting in a wider high-reflection band \cite{Xifre2009}.

On the other hand, different fabrication techniques have been used to obtain omnidirectional (OD) mirrors that operate on the visible and/or near infrared (Vis-NIR) range of the electromagnetic spectrum. For example, Chen et al. \cite{Chen1999},
\notaL{Hay que checar que la puntuación vaya después de las citas,
	para este estilo de citas entre corchetes} reported the fabrication of a 
6-pair TiO$_{2}$/SiO$_{2}$ structure with
an OD band of about 70 nm in the NIR range, employing sol-gel deposition 
method. Park et al. \cite{Park2003}, used molecular beam epitaxy to 
grow a stack of four pairs of GaAs/AlAs layers, followed by its conversion to
GaAs/Al$_{2}$O$_{3}$ layers by selective oxidation of the AlAs 
layers, to obtain an OD with a band from 710 to 950 nm. 
On the other hand, DeCorby et al. \cite{DeCorby2005}, fabricated mirrors by
coupling multiple layers of Ge$_{33}$As$_{12}$Se$_{55}$ chalcogenide glass and
polyamide-imide polymer, deposited by thermal evaporation and spin-casting
respectively, to obtain a 150 nm wide omnidirectional band centered at
1750 nm. Furthermore, Jena et al. \cite{Jena2019},
used sequential asymmetric bipolar pulsed DC magnetron sputtering (for TiO$%
_{2}$ layers) and radio frequency magnetron sputtering (for SiO$_{2}$
layers) to generate TiO$_{2}$/SiO$_{2}$ 1D-PC's and achieved an OD band from
592 to 668 nm. However, these techniques are expensive and they
require sophisticated equipment and long fabrication times. Using PS
is an attractive alternative, since it can be easily manufactured by 
electrochemical etching of crystalline Si in a hydrofluoric 
acid based electrolyte, to obtain a sponge-like nanostructure composed 
of Si and air. By modulating the supplied current and its application 
time during the electrochemical reaction, it is possible to obtain 
multilayer structures allowing for fabrication OD mirrors \cite{Xifre2015,Pavesi2000}.
Although optical filters \cite{Estevez2009,Ariza2014} are the most common
application of PS PC's, they have also been widely used as chemical
sensors \cite{Giusseppe2011,Agarwal2018}, waveguides \cite{Hussel1997} and
for photoluminescence control \cite{Antunez2014}. Recently, the study of
chirped multilayer structures has
increased due to their possible application as flat focusing mirrors \cite{Wu2021,Kozar2017,Cheng2018}.
\notaL{Lens o mirror, no puede ser ambas? De verdad esto es lo que más lo ha popularizado?} 
PS based dielectric optical filters, quasi-OD and OD mirrors have been extensively studied in different
regions of the electromagnetic spectrum, such as the ultraviolet (UV)
\cite{Jimenez2020}, visible \cite{Ariza2012}, and NIR \cite{Bruyant2003} region. 
However, to obtain the desirable high index of refraction
contrast, layers of high porosity have to be employed, which makes the
resulting structures relatively fragile. In addition, use of high porosity makes the fabrication of large structures, with a
very large number of layers, unfeasible. For this reason, in this work
we study different strategies to produce multilayered mirrors
with high reflectance omnidirectional band 
with relatively small thickness and refractive index contrast. 
\notaV{Se omite la frase "Specifically, our aim is to maximize the 
	reflectance $R$ averaged over a wide range of wavelengths $\lambda$ 
	and angles of incidence $\theta$", la idea general esta en la oracion anterior}

This paper is organized as follows. In Sec. \ref{s:theory} \notaL{No uses números,
	usa referencias a etiquetas para numerar y referir todo} we develop the
methods used to design and calculate the reflectance spectra of the PS
multilayered structures such as chirped structures and mirror
stacks. In Sec. \ref{s:exp} we provide details about the
fabrication of these structures. In Sec. \ref{s:res} we present the numerical
and experimental results corresponding to our proposed structures and compare
them to previous reports. We obtained significantly large band-widths
with relatively thinner structures than reported before. \notaL{Dejo para resultados y
	conclusiones los detalles de con quién comparamos y qué salió.}
Finally, we discuss our conclusions in Section \ref{s:conc}.

\section{Numerical simulation} \label{s:theory}

\notaV{Nombre de la sección propuesta por Dr. David}
\notaL{Pon etiquetas a todo para poderlo referir}
\notaV{Parrafos reescritos por Dr. David}

In this paper, two techniques are developed to design 
multilayer photonic structures. In the first, the wavelength 
($\lambda _{j}$), at which the $j$-th period of the structure 
is designed, is modulated by an increasing function. This can 
be as simple or complex as you like. The proposed function was used to
optimize $<$R$>$ with the Minuit module of PDL (Perl Data Language) \cite{minuit}. 
The other technique for proposing highly reflective structures 
over a wide region of the electromagnetic spectrum is to stack
sub-mirrors tuned to different wavelengths. For each 
sub-mirror the dispersion relation is analyzed.

For the analysis of the propagation of electromagnetic fields 
through multilayer systems, we employ the transfer matrix 
method based on Puente-Díaz et al. formalism \cite{Puente2020}. 
In spite some equivalent formulations have been proposed to 
obtain the optical properties of multilayer systems 
\cite{Mochan1987,Ortiz2020,Chavez2020}, here we use a 
recently developed formalism for the numerically stable 
calculation of the reflectance of large multilayer systems. 
Briefly describing, 
we assume a 1D system with variations along the $z$ direction 
and consider an incident linearly polarized beam of light 
(either TE or TM polarization) that propagates throughout 
the structure. The reflectance and transmittance are given by 
$R=|r|^{2}$ and  $T=\beta \left\vert t\right\vert ^{2}$,
respectively, with \cite{Puente2020}
\begin{equation}
	r=\mp \frac{Z_{0}M_{11}+M_{12}-Z_{0}Z_{s}M_{21}-Z_s
		M_{22}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{rBloch}
\end{equation}%
and
\begin{equation}
	t=\frac{2Z_{\zeta
	}}{Z_{0}M_{11}-M_{12}-Z_{0}Z_{s}M_{21}+Z_{s}M_{22}},  \label{tBloch}
\end{equation}%
where $Z_0$ and $Z_s$ are the impedances of the vacuum 
and the substrate, respectively. $\beta =\text{Re}Z_{0}/\text{Re}Z_{s}$ is chosen for 
TE polarization while $\beta=\text{Re}Z_{s}/ 
\text{Re}Z_{0}$ for TM polarization. The upper sign 
$-$ in Eq. (\ref{rBloch}) and the subscript 
$\zeta =s$ in Eq. (\ref{tBloch}) are chosen for 
the case of TE polarization, while the lower sign 
$+$ and the subscript $\zeta =0$ correspond to TM 
polarization. Moreover, sub-index $0$ and $s$ 
refer to the incident and substrate media, respectively.
Furthermore, $M_{ij}$ are the elements
of the transfer matrix which relates
the electromagnetic fields of all interfaces in the structure through

\begin{equation}
\resizebox{\textwidth}{!}{$\displaystyle{
	M=\frac{1}{Z^{+}-Z^{-}} \left( 
	\begin{array}{cc}
		Z^{+}\text{exp}\left( iKD\right) -Z^{-}\text{exp}\left( -iKD\right)  & 
		-2iZ^{+}Z^{-}\sin KD \\ 
		2i\sin KD & Z^{+}\text{exp}\left( -iKD\right) -Z^{-}\text{exp}\left(
		iKD\right) 
	\end{array}%
	\right) \text{.}}$}  
\label{MsBloch}
\end{equation}
%}
In this case, $Z^{\pm }$ can be obtained as 
\begin{equation}
	Z^{\pm }=-\frac{\widetilde{M}_{12}}{\widetilde{M}_{11}-\Lambda _{\pm }}\text{,}  \label{ZBloch}
\end{equation}%
being 
\begin{equation}
	\Lambda _{-}=\frac{1}{2}\text{tr}\widetilde{M}\pm i\sqrt{1-\left( \text{tr}\widetilde{M}/2\right)
		^{2}}\text{,}  \label{LBloch}
\end{equation}%
where the sign that satisfies the relation $\left\vert \Lambda
_{-}\right\vert >1$, and $\Lambda _{+}=\Lambda _{-}^{-1}$ is chosen.
Moreover, tr corresponds to the trace and $\widetilde{M}_{ij}$ $\left( i,j=1,2\right) 
$ denote the elements of the usual transfer matrix $\widetilde{M}$ of the $N$-layer
system, that is, 
\begin{equation}
	\widetilde{M} = \prod \limits_{j=1}^{N}%
	\begin{bmatrix}
		\cos k_{j}d_{j} & iZ_{j}\sin k_{j}d_{j} \\ 
		iY_{j}\sin k_{j}d_{j} & \cos k_{j}d_{j}%
	\end{bmatrix}%
	,  \label{Mcoef}
\end{equation}%
where 
\begin{equation}
	k_{j}=\sqrt{\epsilon _{j}q^{2}-Q^{2}}  \label{kj}
\end{equation}%
is the normal component (to the interfaces) of the wave vector, $Z_{j}$ is
the corresponding surface impedance, $Y_{j}=1/Z_{j}$ is the surface
admittance, $\epsilon _{j}=n_{j}^{2}$ is the permitivity (for simplicity we
assumed all media were nonmagnetic, with permeability $\mu _{i}=1$), $%
q=\omega /c=2\pi /\lambda $ is the free-space wavenumber corresponding to
the wavelength $\lambda $ and 
\begin{equation}
	Q=n_{0}q\sin \theta _{i}  \label{Snell}
\end{equation}%
is the projection of wavevector onto the interfaces, 
which is conserved according to Snell's law, with 
$\theta _{i}$ the angle of incidence. The surface 
impedances are given by $Z_{j}=q/k_{j}$ for TE 
polarization and $Z_{j}=k_{j}/q\epsilon _{j}$ for 
TM polarization. The complex refractive index of the porous layers were 
obtained through the Bruggeman's effective medium 
theory, which has been reported to adequately reproduce 
the PS optical parameters \cite{Giusseppe2011,Pap2006,Estrada2018}.

@@

Some of the proposed photonic structures were synthesized through anodic
etching of a (100) oriented, $p$-type Boron doped, crystalline Si wafer with
resistivity 0.002-0.005 $\Omega \cdot $cm, under galvanostatic conditions
\cite{Canham1990,Escorcia2007}. The electrochemical anodization process was
performed at room temperature, with an electrolyte of aqueous
hydrofluoric acid (HF) (48$\%$ of
wt) and ethanol (99.9$\%$ of wt) in 1:1 volumetric proportion, respectively.
However, as it is not desirable to use very high
porosity contrasts due to structure fragility and electrolyte
diffusivity problems \cite{Ariza2011}, the current
densities were chosen as 35 and 305 $\text{mA}/\text{cm}^{2}$, 
with corresponding porosities of 51\% and 76\%, respectively.
The porosity of the layers was obtained by a previous calibration
curve through a gravimetric technique \cite{Pap2006}. The 
etching rate of PS was obtained by synthetizing single layers under 
similar conditions and measuring their thicknesses through Scanning 
Electron Microscopy (SEM). Absolute reflectivity measurements were 
carried out with a Perkin Elmer Lambda 950 UV/Visible 
spectrophotometer with a variable angle universal reflectance 
accessory (URA) for different incident angles $\theta _{i}=10^{\circ 
}$, $20^{\circ }$, $30^{\circ }$, $40^{\circ }$, $50^{\circ }$ and 
$60^{\circ }$ using non-polarized light. The maximum and minimum 
values of $\theta _{i}$ were constrained by the angular range of the 
equipment accessory URA.

@@

In this section we present optimized calculations of the reflectance
of different multilayered omnidirectional wide-band mirrors and we
compare the results with experimental spectra taken from
the corresponding samples at several angles of
incidence. Sec. \ref{ss:chirped} is devoted to chirped-type Bragg
mirrors while Sec. \ref{ss:stacked} is devoted to structures made of
stacked sub-mirrors.

\subsection{Chirped-type Bragg mirrors}\label{ss:chirped}
